---
title: "Shiny Application and Reproducible Pitch"
author: "Aswin"
date: "June 11, 2018"
output: slidy_presentation

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Course Project description :

This is the final course project for the Developing Data Products Course. The project consists on two parts:

1. Shiny app with supporting documentation

2. Presentation made through Slidify to pitch the above shiny app

## The Data set : **hills**

I have taken the data set **hills** from the **MASS** library.

It contains the following data :

```{r}
library(MASS)
head(hills)
```

The data set contains 4 columns and 35 rows.

## Model used.

We used lm to fit a linear model based on **hills** dataset

```{r}
library(ggplot2)
plot(x=hills$dist, y=hills$time, main="Distance  - Time",xlab = "Distance",ylab="Time")
fit <- lm(hills$time ~ hills$dist + hills$climb , data=hills)
summary(fit)
abline(fit,col="red")
```

## About Shiny App

1. server.R : Graph is updated automatically by monitoring the sliders for changes in user input.The files can be found here : https://github.com/Aswin025/Shinyapps

2. UI.R : Slider input is used to change distance and climb to estimate time taken to climb a mountain.The App can be found here : https://aswin025.shinyapps.io/TimePrediction/





